Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-13 xrb2/paper.tex
Added quadratic curve equation to section 3.2

Figure~\ref{fig:flame_speeds_1} gives the position of the flame front as a function of time for the $\tt{F500}$ and $\tt{F1000}$ runs 
(blue and orange, respectively) to show the dependence on rotation rate. {\color{blue}In 
\citet{flame_wave1}, we 
applied a linear least-squares fit to the flame front position as a function of time to estimate the propagation velocity. 
For this study we instead fit a quadratic curve to each set of data, as some of the hotter $500~\mathrm{Hz}$ 
runs exhibit significant acceleration. We discarded the data points with $t \lesssim 20~\mathrm{ms}$, 
since these correspond to the initial transient period before the flame has begun to propagate 
steadily.} The fit parameters yield estimates of the flame acceleration and velocity at $t = 0~\mathrm{ms}$, 
which are provided in Table~\ref{table:flame_speeds}. {\color{blue}Note that the listed velocity is 
only 
a parameter that may be used to calculate the flame speed at an arbitrary time. It is not an 
estimate of the true initial velocity of the flame, since the flame has not achieved ignition yet 
at $t = 0~\mathrm{ms}$. We use the fit parameters to calculate the flame speeds at $t = 50~\mathrm{ms}$ (when the flame has reached steady propagation), given in the fourth column of Table \ref{table:flame_speeds}.} \MarginPar{KE: Outside of updating the data in the table, is there anything else we 
want to add to this para?}

>>>>

Figure~\ref{fig:flame_speeds_1} gives the radial position of the flame front as a function of time 
for the $\tt{F500}$ and $\tt{F1000}$ runs (blue and orange, respectively) to show the dependence on 
rotation rate. In \citet{flame_wave1}, we applied a linear least-squares fit to the flame front 
position as a function of time to estimate the propagation velocity. As some of the flames in this 
set of simulation runs exhibit significant acceleration, for this study we instead fit the data 
with a quadratic curve of the form:
\begin{equation}
	\label{eq:quadratic_fit}
	\color{blue} r(t) = \half a t^2 + v_0 t + r_0
\end{equation}
\noindent The parameter $a$ is the acceleration of the flame, $v_0$ is the velocity at $t = 
0~\mathrm{ms}$, and $r_0$ is the position at $t = 0~\mathrm{ms}$. We do not include the data points 
with $t \lesssim 20~\mathrm{ms}$ when performing the fit, since these correspond to the initial 
transient period before the flame has begun to propagate steadily. The values of $a$ and $v_0$ for 
the full suite of simulation runs are provided in Table~\ref{table:flame_speeds}. Note that $v_0$ 
is only a parameter that may be used to calculate the flame speed at an arbitrary time. It is not 
an estimate of the true initial velocity of the flame, since the flame has not achieved ignition 
yet at $t = 0~\mathrm{ms}$. We use the fit parameters to calculate the flame speeds at $t = 
50~\mathrm{ms}$ (when the flame has reached steady propagation), given in the fourth column of 
Table \ref{table:flame_speeds}.
